analysis-pilot

### 2023-08-01 code/analysis-pilot.Rmd
15:46 update

ggplot(data = accuracy, aes(y = game, x = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#228B22", width = .7) +
  geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("Percentage Accuracy") +
  ylab("Game ID") +
  theme(aspect.ratio = 4/5,
        axis.title = element_text(size=14,face="bold"),
        axis.text = element_text(size=12),
        legend.position = "none")
```

>>>>

ggplot(data = accuracy, aes(x = percent, y = game)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#228B22", width = .7) +
  geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("Percentage Accuracy") +
  ylab("Game ID") +
  theme(aspect.ratio = 4/5,
        axis.title = element_text(size=14,face="bold"),
        axis.text = element_text(size=12),
        legend.position = "none")
```
